Curve counting in genus one: elliptic singularities {\it \&} relative geometry

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
added a line to intro re: fictitious markings

>>>>

\tred{We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.}
